 



```{r}
setwd("/Users/gauravpuri/Downloads/Master Thesis Readings /")
credit <- read.csv("german_credit.csv", header = TRUE, sep = ",")

#code to convert variable to factor
credit$Creditability <-as.factor(credit$Creditability)

#code to convert to numeric
credit$Age..years. <-as.numeric(credit$Age..years.)

#code to convert to decimal
credit$Credit.Amount<-as.double(credit$Credit.Amount)

credit$Credit.Amount<-as.factor(ifelse(credit$Credit.Amount<=2500,'0-2500',ifelse(credit$Credit.Amount<=5000,'2600-5000','5000+')))

```

Creating train and test datasets by divding the datasets into two parts.

```{r}
d = sort(sample(nrow(credit), nrow(credit)*.6))
#select training sample
train<-credit[d,]
test<-credit[-d,]
train<-subset(train,select=TRUE)

```

Train the model on linear regression for Creditability feature. 

```{r}
m<-glm(Creditability~.,data=train,family=binomial())
```

Calculating ROC Curve for model
There is a strong literature based showing that the most optimal credit scoring cut off
decisions can be made using ROC curves which plot the business implications of both the
true positive rate of the model vs. false positive rate for each score cut off point (Beling et
al, 2005)

```{r}
#load library
library(ROCR)
#score test data set
test$score<-predict(m,type='response',test)
View(test$score)
pred<-prediction(test$score,test$Creditability)
perf <- performance(pred,"tpr","fpr")
plot(perf)
```

Calculating the top features on which creditability depends.

```{r}
#get results of terms in regression
g<-predict(m,type='terms',test)
#function to pick top 3 reasons
#works by sorting coefficient terms in equation
# and selecting top 3 in sort for each loan scored
ftopk<- function(x,top=3){
  res=names(x)[order(x, decreasing = TRUE)][1:top]
  paste(res,collapse=";",sep="")
}
# Application of the function using the top 3 rows
topk=apply(g,1,ftopk,top=3)
```

```{r}
test<-cbind(test, topk)

library(rpart)
fit1<-rpart(Creditability~.,data=train)
plot(fit1);text(fit1, font = 0.1 );
```

